### 2018-10-12 Manuscript/Manuscript.tex

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{\textbf{LIP area through the tropics through time
Panel A) ice extent
Panel B) all latitude 
Panel C) in the tropics (different models)
Panel D) heat map of one of the models}}
	\label{fig:LIP_area}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{Manuscript/Figures/LIP_Areas.pdf}
	\caption{\textbf{A) paleolatitude of emplacement and the initial area estimate of each LIP in the compilation.
    B) total LIP area through time for the different post-emplacement models.
    C) tropical LIP area through time for the different post-emplacement models.
    D) heat map for one of the models showing the latitudinal distribution of LIP area.
    E) latitudinal extent away from the poles of land ice through time.}}
	\label{fig:LIP_area}
\end{center}
\end{figure}
